The Journey from Wild to Textbook Data: A Case Study from the National Longitudinal Survey of Youth

### 2021-09-29 paper/paper-jsdse/paper-jsdse.tex
warning text about textbook data not being the best textbook data and future updates possible to come

\noindent%
{\it Keywords:}  Data cleaning; Data tidying; Longitudinal data; NLSY79; Open data; Initial data analysis; Outlier detection; Robust linear regression
\vfill

@@

>>>>

\noindent%
{\it Keywords:}  Data cleaning; Data tidying; Reproducible workflow; Longitudinal data; NLSY79; Initial data analysis;
\vfill

@@

Some readers may disagree with our decisions made to produce the refreshed textbook data and may have better insight than us in producing a more appropriate textbook data. We do not assert that we have produced the best textbook data, but rather we describe our journey to provide a reasonable textbook data. All code and documentation are provided for transparency and future updates of \texttt{yowie} package may contain additional versions of the data if we come to have better understanding of a valid data.

### 2021-09-29 paper/paper.Rmd
warning text about textbook data not being the best textbook data and future updates possible to come

>>>>

Some readers may disagree with our decisions made to produce the refreshed textbook data and may have better insight than us in producing a more appropriate textbook data. We do not assert that we have produced the best textbook data, but rather we describe our journey to provide a reasonable textbook data. All code and documentation are provided for transparency and future updates of `yowie` package may contain additional versions of the data if we come to have better understanding of a valid data.
